Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-05 AO_bondedSi.tex
edits from DTJ to Figure 2 caption

The reflectivity $R$ (Equation \ref{Eq:FresnelR}) is about 30\% in the wavelength range 1100 to 5000 nm.  We define the coefficient of finesse\verb|\cite{2007fuph.book.....S}|, $F$ (Equation \ref{Eq:coeffF}), in the customary way to encapsulate the Fabry-P\`{e}rot etalon's dependence on reflectivity.  The coefficient of finesse is shown in the right panel of Figure \ref{figSiIndexFinesse}.  Si is negligibly absorbing longward of about $\lambda$ = 1200 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses, as shown in Figure \ref{figSiAbsorbfig}.  Figure \ref{figSiAbsorbfig} also verifies a key assumption that we will make when comparing the transmission of Si substrates of different heritage and thickness.  Specifically DSP Si pucks and wafers have the indistinguishable transmission longward of 1250 nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1200 nm.  \verb|\cite{2006SPIE.6273E..77F}| cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/fpAbsorbfig}}
\caption{Ratio of transmissions of Si wafers of different thicknesses, specifically the transmission of a thin ($\sim0.5$ mm) Si wafer divided by that of a 3 mm thick Si puck.  Both samples were double side polished.\label{figSiAbsorbfig}  The transmission scatters about 1.0 in wavelength ranges for which Si is negligibly absorbing for a path length ratio of $\sim$6, and exceeds 1.0 in wavelength ranges for which Si absorption is detected. The left panel shows that Si is firmly absorptive shortward of $\lambda \; =$ 1200 nm.  The right panel shows the absolute deviation from unity on a log scale.  The typical uncertainty and drift per measurement is about 0.2\%.  Absorption is detected at 0.4\% at $\lambda \;=$ 1200 nm.}
\end{figure}

>>>>

The reflectivity $R$ (Equation \ref{Eq:FresnelR}) is about 30\% in the wavelength range 1100 to 5000 nm.  We define the coefficient of finesse\verb|\cite{2007fuph.book.....S}|, $F$ (Equation \ref{Eq:coeffF}), in the customary way to encapsulate the Fabry-P\`{e}rot etalon's dependence on reflectivity.  The right panel of Figure \ref{figSiIndexFinesse} shows the coefficient of finesse as a function of wavelength for $T = 295\;$K and $T = 77\;$K.  Si absorbs negligibly longward of $\lambda$ = 1250 nm, which we verified by comparing the transmission of Si reference samples of different thicknesses (Figure \ref{figSiAbsorbfig}).  We computed the ratio of transmissions of double side polished Si wafers of different thicknesses.  Specifically, we evaluated the transmission ratio at each wavelength bin from 1000 to 2500 nm, from the transmission of a thin ($\sim0.5$ mm) Si wafer divided by that of a 3 mm thick Si puck.  Absorption is detected shortward of 1250 nm.  Figure \ref{figSiAbsorbfig} verifies a key assumption that we make when comparing the transmission of scrap Si of different provenance and thickness.  Specifically, double side polished 3 mm thick Si pucks and 0.5 mm thick Si wafers have indistinguishable transmission at the $<0.2$\% level longward of 1250 nm.  The Si refractive index is indistinguishable from sample to sample for the wavelength ranges we care about- the non-absorbing wavelengths greater than about 1250 nm.  \verb|\cite{2006SPIE.6273E..77F}| cites the wide variety of values for refractive index from the literature as evidence that batch-specific Si should be used as reference for cases in which absolute accuracy greater than $\pm5\times10^{-3}$ is desired.  An absolute deviation of $\pm5\times10^{-3}$ in refractive index corresponds to a Fresnel transmission difference of about 0.2\%, which is comparable to our measurement uncertainty.  In the next subsection we work out the wavelength dependent transmission for the air etalon.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/fpAbsorbfig}}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda \; =$ 1250 nm.  We assume spectral regions longward of 1250 nm are non-absorptive.  The correlated and heteroscedastic measurement errors are typically less than 0.2\%.}
\end{figure}
